Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-13 documentation/paper.tex
Wrote initial abstract

\begin{abstract}
    TODO, once content is affirmed.
\end{abstract}

>>>>

\begin{abstract}
    Background radiation is a major hurdle to overcome for bubble chamber dark matter experiments such as PICO-60. The current practice of manually developing a discriminator function to eliminate background data is difficult when calibration data is frequently impure and present only in small quantities. In this study, several different input formats and neural network architectures are applied to the task. First, they are optimized in a supervised learning context. Next, novel semi-supervised learning algorithms are trained, and found to replicate the Acoustic Parameter discriminator previously used in PICO-60 with up to 100\% accuracy.
\end{abstract}
